Turbulence in compact to giant HII regions

### 2021-11-19 strucfunc_paper.tex
Javier changes 2021-11-19

% Abstract of the paper
\begin{abstract}
  Fluctuations of centroid velocities on the plane of the sky are a powerful tool for studying the turbulent dynamics of emission line regions.
  To characterize these fluctuations we apply a statistical analysis using the second-order structure function to archival \halpha\ observations of a diverse sample of 9 \hii{} regions.
  This regions are located in the Milky Way and other Local Group galaxies, and
  span more than two orders of magnitude in size and luminosity.
  By fitting a simple functional form of the structure function to our results
  we extract three parameters related to the fluctuations in each region: the
  total velocity dispersion \(\sigma\), which spans from 3 to 15 km s\(^{-1}\), the
  autocorrelation length \(r_0\), which covers 0.06 - 8 pc, and the power-law slope \(m\), which ranges from 0.82 to 1.95.
  The velocity dispersion is found to correlate primarily with luminosity,
  while the autocorrelation length correlates primarily with the size of the region.
  The power-law slope shows an apparent correlation with distance,
  but this is probably an artifact of poor spatial resolution for the most distant regions.
  A comparison between \(\sigma\) and \(\sigma_{POS}\) shows that this last value is at roughly the double for all regions.
  \textbf{Add a sentence about the conclusions!}
  % We study the turbulent velocity fluctuations in the ionized gas of four giant HII regions using the radial velocity field in the H$\alpha$ emission line. The data was acquired by long-slit spectroscopy and Fabry-Perot observations obtained with the William Herschel Telescope. Each velocity sample is statistically analyzed with the second order structure function. The correlations in our results shows evidence that the velocity field can be consider in a turbulent state. This turbulent motions are described by a power-law with a mean index of 1.7 for different sized regions at different distances. The physical interpretation of the power-law behavior consider that an energy cascade is taking place in the photoionized gas.
\end{abstract}

% Select between one and six entries from the list of approved keywords.
% Don't make up new ones.
\begin{keywords}
HII regions -- ISM
\end{keywords}

@@

It is known that the speed of sound in a HII region is of the order of \(c_{HII} \sim\) 13 km s\kms.
\citet{smith1970} discovered that the probable velocities of internal motions of extragalactic HII regions, \(\sigma_{W}\) (line width integrated over the whole HII region), were in the range of $\sim$ 19-34 km s\kms\ covering supersonic values.
\citet{skillman1984kinematics} found broad profiles in giant extragalactic HII regions (GEHRs) that have a FWHM\(>\)30km s\kms. 
This property is mainly used to distinguish between 'normal' and 'giant' HII regions. Other differences are their size, luminosity and their stellar population. 
For the velocity to be supersonic it is necessary a continuous mechanism to maintain the observed motions, as supersonic motions are expected to dissipate energy via shocks \citep{1994Ap&SS.216..285C}.
Also, this non-thermal broadening on the spectral emission lines has been suggested as evidence of disorder motions along the line-of-sight (LOS) of the ionized gas. 
Turbulence is suggested as a mechanism that can stir the medium and maintain the supersonic velocities. 
The large lengths of astrophysical objects, ranging in scales from 10$^{6}$ to 10$^{17}$ m \citep{2010ApJ...710..853C}, and the high Reynolds numbers (Re), in the order of 10$^{4}$ - 10$^{9}$, are the main properties that supports the idea of a turbulent interstellar medium.
Previous studies \citep{1999intu.conf.....F,2004ARA&A..42..211E,scalo2004interstellar} revealed that different phases of the interstellar medium show fluctuations on their velocity field that can be interpreted as evidence of random motions.

The usual picture considers that interstellar turbulence is driven on different scales by various energetic processes.
Also, it is thought that the formation of structures like filaments and shells in the diffuse medium is determined by large-scale turbulence.
Stars are the mainly mechanism proposed to account for the large input of kinetic energy through UV radiation, but the dominant energetic sources and their relation to turbulence still is unclear.

\citet{melnick1977,terlevich1981} were the first to shown an empirical relationship between the line width and the integrated properties of the HII regions as the diameter or the luminosity ($r \sim \sigma ^{\sim 2}$ ; $L_{H} \sim \sigma ^{\sim 4}$).
They conclude that GEHRs follow this relations as self-gravity systems like globular clusters or elliptical galaxies.
The work of \citet{1988A&A...201..199A} confirmed these relationships considering the discrepancies of previous investigations obtaining \(L_{H_{\alpha}} \propto \sigma^{3.9}\) and \(r \propto \sigma^{1.84}\).
\citet{2012MNRAS.422.3339W} have found that clumps and HII regions follow scaling relations over the range of z = 0-2 for \halpha\ size, velocity dispersion, luminosity and mass finding \(\sigma \propto r^{0.42}\), \(L_{H_{\alpha}} \propto r^{2.72}\) and \(L_{H_{\alpha}} \propto \sigma^{4.18}\). This results imply that the same process are seen at high redshifts and the current epoch in star forming regions. \citet{2015MNRAS.449.3568M} found that the relation is also found in dwarf galaxies with a \(L_{H_{\alpha}} \propto \sigma^{5}\).

The idea of a virial system has been developed by \citet{1993ApJ...418..767T,munoz1996} into the \textit{Cometary Stirring Model} (CSM) with the aim to separate the mechanism that contribute to the line broadening.
The stellar winds also tend to be used for an explanation of the line broadening and turbulence in GEHRs \citep{1994ApJ...425..720C}.
This features seems to drive visually the regions with filaments, arcs and shells.
On their spectra double and multiple emission features are signature of these objects.
\citet{2020MNRAS.494...97S} argue that winds on ionizing clusters in GEHR must merge into a hot cluster because of the close proximity of the massive stars.
\citet{2019ApJ...871...17U} propose that stellar feedback is an important source of energy to maintain turbulence in nearby galaxies.

The classic turbulence theory \citep{kolm1} assumes a three-dimensional isotropic, incompressible and subsonic flow where an energy cascade is taking place.
The interstellar matter does not have those physical properties and our observations are in two-dimensions.
But as mentioned above the idea of an energy cascade is used to understand our observations.
The energy cascade goes from the largest vortices where the energy in injected until it reaches dissipation with the smallest vortices.
In the energy cascade three scales are defined based on their Reynolds number.
The energy injection scale (Re $\rightarrow \infty$), $L_{EI}$, the dissipation scale (Re $\rightarrow$ 1), $L_{D}$ and the inertial scale, $L_{I}$, between the previous two.
Since the energy distributions depends on the scale, the energy cascade concept is described with an energy spectrum, $E(k) \propto k$ where $k$ is the wave number for a determined scale $l$ ($k \equiv r^{-1}$).

The fluctuations associated with the centroid velocities on the plane-of-sky (POS) of photoionized regions have been characterized several times using the second order structure function (the Fourier transform of the energy spectrum, $E(k)$).
This studies span from galactic HII regions \citep{1986ApJ...300..624R} like Orion \citep{von1951methode,munch1958internal,castaneda1988,1992ApJ...387..229O,arthur2016turbulence} to giant HII regions \citep{1961MNRAS.122....1F,lagrois2009multi,lagrois2011}, like NGC 604 in the M 33 galaxy \citep{tanco1997,2019arXiv191203543M}.

The procedure using the structure function allow us to determine a distinction between homogeneous turbulence and pure random velocity fluctuations in the photoionized gas, but despite the previous evidence of this fluctuations not been random, little is understood about their nature.
Several problems arise in the study of these fluctuation.
Intrinsic with observations there is the projection of a three-dimensional function into the plane-of-sky \citep{von1951methode,munch1958internal}.
Other statistical techniques like velocity channel analysis (VCA) \citep{2000ApJ...537..720L} have been proved to better recreate the spectrum of the velocity field \citep{medina2014,arthur2016turbulence}.
More recently, the structure function was used with full 6D measurements (position-velocity) to study the motions of stars in the Orion Molecular Cloud Complex.
\citet{2021ApJ...907L..40H} argue that newborn stars should reflect the turbulent kinematics of their natal clouds.
Using this previous method they are free of the projected element that interfere with previous gas-based studies and their results agree with the scaling law proposed by \citet{1981MNRAS.194..809L}.

Despite different issues that are related with the nature of the problem of turbulence in HII regions, the vast majority of research using the second-order structure function consider individual regions and hence different methodology.
\citet{1987ApJ...317..686O} has determined the structure functions for a sample of galactic HII regions but isn't conclusive about them.
The individuality of previous works and the need to understand the relationship between the measured turbulent properties for different classes of HII regions has lead us to develop this investigation.

Using archival data we perform the second-order structure function on a sample of HII regions.
Our sample spans in size from 4 pc to 400 pc and has luminosities between 10\(^{37}\) - 10\(^{39}\) erg s\(^{-1}\); from galactic to extragalactic HII regions.
We apply an uniform methodology of a functional form of the structure function to characterize the turbulent using the  autocorrelation length, \(r_0\), and power-law slope, \(m\).
Our results are compared with physical properties of each region and are also compared with previous investigations.
With this work we aim to fill a gap with an uniform statistical analysis of turbulence between galactic and giant HII regions.

The paper follows the next order: in Section \ref{sec:HIIsample} we describe the observational data and some main kinematics properties of each region. In Section \ref{sec:met} we present the statistical method used in this work. Section \ref{sec:results} presents the structure function of each region along with the turbulent parameters obtained by a non-linear regression method. In Section \ref{sec:discussion} we discuss our findings in the context of previous works.

@@

We use previous published observational data to measure the second-order velocity structure function for a number of nine HII regions. 
Table \ref{tab:Reg} shows the HII regions names
with the main physical properties of each region. 
These regions are located in the Milky Way, the Magellanic clouds and in the M 33 and NGC 6822 galaxies.

@@

Orion is a galactic HII region located at a distance of 440 pc \citep{2008AJ....136.1566O}.
The main ionizing star is \(\theta^{1}\)Ori C (spectral type \(\sim\)O7) with fast stellar wind, and 3 B-type stars from the Trapezium cluster.
The position of Orion near the side of the Orion Molecular Cloud (OMC-1) make it an ongoing star formation region and a example of a blister HII region \citep{arthur2016turbulence}.
Its physical and kinematics properties along its stellar population are well documented in the review of \citet{2001ARA&A..39...99O}.

We use data from \citet{1987A&A...176..347H} and \citep{arthur2016turbulence} to study of turbulence in the Orion Nebula.
\cite{1987A&A...176..347H} observations were obtained using a 106 cm-Cassegrain telescope at Observatorium Hoher List. 
A Fabry-Pérot interferometer was used having the étalon a separation of 0.5 mm. 
Interferograms have been taken with different pointing directions of the telescope's optical axis in the nebula. 
The exposures are overlapped and fall into one square of a grid with a width of 1' centered at \(\theta^{1}\)Ori C.

\citet{arthur2016turbulence} observations were initially published by \citet{2008RMxAA..44..181G}. The data were obtained with the echelle spectrograph attached to the 4 m telescope at Kitti Peak National Observatory. These observation cover 3 \(\times\) 5 arcmin\(^{2}\)of the Orion nebula and the data consist of 96, 300 arcsec North-South orientated slits at 2 arcsec intervals with a width of 0.8 arcsec. The velocity resolution is 8 km s\(^{-1}\).

The Carina nebula is located at a distance of 2.35$\pm$0.05 kpc \citep{2006ApJ...644.1151S}.
Young clusters like Trumpler 14 and 16, and Collinder 228 together form the Car OB1 association.
This OB association has more than 65 stars earlier than B0, and several Wolf-Rayet stars.
The most star is a luminous blue variable, $\eta$ Car \citep{Damiani:2016a}.
The stellar content has lead to identify the Carina nebula as a star formation region, and as such it presents several phenomena related with young stras as (\citet{2006ApJ...644.1151S} and reference therein): evaporating protoplanetary discs, erosion of large dust pillars and the triggering of a second generation of embedded stars, Herbig-Haro objects, to mention some. 
All of these phenomena are consequence of the UV radiation and stellar winds from star clusters in the HII region.

The Lagoon Nebula (M8, NGC6523) is located at a distance of 1 250 pc \citep{2005A&A...430..941P} and contains the young stellar cluster NGC6530.
The region is illuminated by different massive stars of spectral types O and B, the hottest being 9 Sgr, type O4V \citep{Damiani:2017b}.
Optically, the brightest part of the nebula is called 'Hourglass nebula' which surrounds and obscures the star Herschel 36, type O7 \citep{1986AJ.....91..870W}. 
The velocity field shows several expanding shells, related to the cluster NGC 6530, the O stars 9 Sgr and Herschel 36, and the massive protostar M8East-IR. A blueshifted, neutral layer is also in very good agreement with predictions of champagne-flow models of blister HII regions \citep{Damiani:2017b}.

Archival data from \citet{Damiani:2016a} and \citet{Damiani:2017b} are use to study the Carina nebula and Lagoon nebula, respectively. 
The ESO VLT/FLAMES multi-fiber spectograph was used for observations (Gaia-ESO Survey internal release \(iDR4\)) of Lagoon nebula  and Carina nebula \citep{2002Msngr.110....1P}. 
Mainly the spectra were obtained with the Giraffe HR15N setup (\(R \sim19 000\), wavelength range 6444-6818 A) which allow to observe \halpha\ emission line. 
The Survey targets are low-mass stars ranging down to magnitude V \(\sim\) 18.5.

Using observations from \citet{Castro:2018a} (private communication) we study the Tarantula Nebula (30 Doradus).
This nebula us located in the LMC (Large Magellanic Cloud) at a distance of 49.9 kpc \citep{2013Natur.495...76P} and is the most luminous star-forming complex in the Local Group \citep{1984ApJ...287..116K}.
It host the star forming region NGC 2070 that contains the massive star cluster R136.
NGC 2070 was observed as part of the MUSE SV (Science Verification) programme at the Very Large Telescope (VLT). 
Four overlapping fields, each with an individual field of 1' \(\times\) 1' and a pixel scale of 0.2''/pixel were observed. 
The data were reduced using the MUSE pipeline based on ESOREX recipes, with final astrometric calibration using the catalogue of \citet{1999A&A...341...98S}. 
The final spectra span 495-9366 A, with a resolving power of \(R \sim3 000\) around \halpha\  \citep{Castro:2018a}.

NGC 346 is the most active star-formation region in the SMC (Small Magellanic Cloud) located at a distance of 60 kpc. 
It has more than 30 O stars that ionize N66, the largest HII region \citep{2011ApJ...740...10D}.
\citet{2008ApJ...688.1050G} propose an expanding H II region or bubble blown by the winds of the massive progenitor as a mechanism that shapes the recent star formation in this region in addition to the photoionizing process of the OB stars. 
This mechanism is similar to shell-like H ii regions, with a central cluster in a cavity, and with ongoing star formation triggered around their periphery.

\subsection{Regions in M33 and NGC 6822}

NGC 604 is the brightest giant HII region in the M33 galaxy visually dominated by a big loop, many shells and different size filaments.
It is located at the distance of 840 kpc (1'' = 4.1 pc) \citep{2015KamKinematics} with a length of 400 pc.
It has a luminosity in L$_{H_\alpha}$ = 10$^{39.42}$ erg s$^{-1}$ \citep{2002MNRAS.329..481B} and in L$_{X}$=9.3$\times$ 10$^{35}$ erg s$^{-1}$ \citep{2008ApJ...685..919T}.
\citet{2012ApJ...761....3M} derive an average age of 4$\pm$1 Myr and a total stellar mass of 1.6$^{+1.6}_{-1.0} \times$ 10$^{5}$M$_{\odot}$ for the region.

The stellar population has been identified and classified by \citet{1996ApJ...456..174H} (and references therein).
Recently, \citet{2011MNRAS.411..235E} focused on studying the Wolf-Rayet (WR) and red super giants (RSGs) stars population.
\citet{2012AJ....143...43F} focused on the massive young stellar objects (MYSOs).
 The average ages for the stars, was determined to be from 3 to 5 Myr \citep{1996ApJ...456..174H} and with the RSGs as an older population have an age of 12.4 $\pm$ 2.1 Myr \citep{2011MNRAS.411..235E}.
This suggest that two episodes of star formation, at least, have taken place in the GEHR.
\citep{1984A&A...141...49H} identified a gradient from the west to the SE of the nebula of 30 km s$^{-1}$.

NGC 595 is the second brightest giant HII region in the M33 galaxy.
The electronic temperature is 7,670 $\pm$116 K \citep{2010MNRAS.402.1635R}.
\citet{1983A&A...119..185V} made an estimate of the total masses of HI and HII in the nebula to obtain values of M$_{HI}=$ 1.2 $\times$ 10 $^{6}$ M$_{\odot}$ and M$_{HII} =$ 4.6 $\times$ 10 $^{5}$ M$_{\odot}$, and a ionizing luminosity of the star cluster is estimated at 5 $\times$ 10$^{50}$ erg s $^{1}$.
\citet{1996AJ....111.1128M} estimate an age of 4.5 Myrs consistent with \citet{1993AJ....105.1400D}.

It has approximately 250 stars of the OB type, 13 Supergiants and 9 WR \citep{1996AJ....111.1128M}, ten WRs confirmed with spectroscopy \citet{1993AJ....105.1400D}, nine of the WN type and a WC, located near the bright core of the region.

The dwarf irregular galaxy, NGC 6822, is located at a distance of 500 kpc (1'' = 2.4 pc) \citep{1996AJ....112.1928G} and the brightest HII regions are Hubble V (HV) and Hubble X (HX).
HV has a characteristic length of 100 pc and a luminosity at its core of in L$_{H_\alpha}$ = 1 $\times$ 10$^{49}$ H$\alpha$ photons s$^{-1}$ \citep{1999PASP..111.1382O}.
HX has a characteristic length of 140 pc and a luminosity at its core of in L$_{H_\alpha}$ = 2.4 $\times$ 10$^{49}$ H$\alpha$ photons s$^{-1}$ \citep{1999PASP..111.1382O}.

%Two recognized OB associations \citep{1991ApJ...379..621H,1992AJ....104.1374W} are identified within the region of HV and HX. HV is located near 'Hodge OB 8', and HX is located near 'Hodge OB13'  \citep{1999PASP..111.1382O}.

The archival data used in this work for the extragalactic giant regions was obtained with the Fabry Perot TAURUS-II instrument in the 4.2-m William Herschel Telescope (WHT) of del Roque de los Muchachos Observatory (ORM) in La Palma, Spain and was retrieved from the La Palma archive\footnote{\url{http://casu.ast.cam.ac.uk/casuadc/ingarch}}.
\citet{sabalisck1995supersonic} mentioned the main aspects of the observations (1990 July 31).
The two-dimensional imaging spectroscopy was captured using an IPCS-II detector and the 125 $\mu$m etalon.
The cumulative integration time per frame is 36 s with a seeing value of 1''.
The format of the data cube was of 256*256*100 with a spatial scale of 0.26 pixel$^{-1}$.
Finally, the reduction and analysis was done with the packages TAUCAL y TAUFITS \citep{1992ASPC...25..445L}.
The NGC 604 TAURUS-II observations were used by \citet{sabalisck1995supersonic}, \citet{tanco1997} and \citet{2019arXiv191203543M}.

%\citet{2002MNRAS.329..481B} 39.42 38.95 38.21 38.30  39.46 37.36  37.08

>>>>

% Abstract of the paper
\begin{abstract}
  Fluctuations of centroid velocities on the plane of the sky are a powerful tool for studying the turbulent dynamics of emission line regions.
  To characterize these fluctuations we apply a statistical analysis using the second-order structure function to archival \halpha\ observations of a diverse sample of 9 \hii{} regions.
  This regions are located in the Milky Way and other Local Group galaxies, and
  span more than two orders of magnitude in size and luminosity.
  We proposed a functional form of the structure function that takes into account the observational seeing, the instrument noise and the size of the observational box.
  By fitting this functional to our results we extract three parameters related to the fluctuations in each region: 
  the total velocity dispersion \(\sigma\), which spans from 3 to 15 km s\(^{-1}\), the
  autocorrelation length \(r_0\), which covers 0.06 - 8 pc, and the power-law slope \(m\), which ranges from 0.7 to 1.3.
  The velocity dispersion is found to correlate primarily with luminosity,
  while the autocorrelation length correlates primarily with the size of the region.
  A comparison between \(\sigma\) and \(\sigma_{POS}\) shows that this last value is at roughly the double for all regions.
  We found that our proposed functional form describe with more accuracy the inertial range and our methodology guarantees consistency for comparison between the galactic and giant HII regions.
  \textbf{Add a sentence about the conclusions!}
\end{abstract}

% Select between one and six entries from the list of approved keywords.
% Don't make up new ones.
\begin{keywords}
HII regions -- ISM: kinematics and dynamics -- turbulence
\end{keywords}

@@

HII regions are far from been static objects.
Initially, the gas of a HII region is ionized in a previously disturbed medium.
When the formed star starts emitting, the energy and matter coming from it interacts with the surrounding medium, putting in motion a series of dynamical processes that have a considerable effect in the velocity field of the HII regions.
Different investigations have shown a complex velocity structure particularly to each region. 
Mainly, the excess in the thermal broadening on the spectral lines is interpreted as disorder motions along the line-of-sight (LOS).
Motions like the expansion or rotation of the region can be accounted for, but after these are considered, still persist a random velocity component in the region.
It has become customary to investigate this random component as turbulence in the ionized gas.

The fluctuations associated with the centroid velocities on the plane-of-sky (POS) of photoionized regions have been characterized several times using the second order structure function.
This studies span from galactic HII regions \citep{1986ApJ...300..624R} like Orion \citep{von1951methode,munch1958internal,castaneda1988,1992ApJ...387..229O,arthur2016turbulence} to giant HII regions \citep{1961MNRAS.122....1F,lagrois2009multi,lagrois2011}, like NGC 604 in the M 33 galaxy \citep{tanco1997,2019arXiv191203543M}.

The procedure using the structure function allow us to determine a distinction between homogeneous turbulence and pure random velocity fluctuations in the photoionized gas.
Several problems arise in the study of these fluctuation.
One of them is that there is no well-established theory for turbulence in astronomical conditions, these being that the medium is compressible and supersonic, and will result in the presence of shock waves \citep{lagrois2011,arthur2016turbulence}.
On the other hand, it is known that these regions are created on the edge of molecular clouds, so they will reach a blister or champagne phase, introducing large-scale gradients not related with random motions \citep{Mivi1995}.
Intrinsic with observations there is the projection of a three-dimensional function into the plane-of-sky \citep{von1951methode,munch1958internal,1964SvA.....8..210K} leading to a loss in information.

There are also a series of problems related to the observations that to date have not been formally addressed like the previous ones.
These problems are that: 1) following observations, there is the seeing and noise due to the telescope and instrument, and 2) that the observations are mostly limited to only one part of the nebula.
This has the consequence that when analyzing a turbulent field, the velocity fluctuations related to small and large scales will be affected due to artifacts introduced by the problems mentioned above.
In turbulence theory, the largest and smallest scales are the most important as they relate to the energy transfer of the turbulence spectrum, which implies that it is necessary to consider them for a correct characterization of the turbulence in the velocity field.
Disregarding the above has led previous investigations in HII regions to erroneous conclusions about the nature of this energy spectrum.

To face these problems, we study the effects of seeing, noise and observational box size in an artificial velocity field to develop and propose a correct form that fits the results of a statistical analysis of the field of velocity of HII regions.
This aims to leave little room for the interpretation of results and to characterize in a more precise way the turbulence in ionized nebulae, something that has not been considered in previous works.
Also, we aim to fill a gap with an uniform statistical analysis of turbulence between galactic and giant HII regions.

Using archival data we perform the second-order structure function on a sample of HII regions.
Our sample spans in size from 4 pc to 400 pc and has luminosities between 10\(^{37}\)-10\(^{39}\) erg s\(^{-1}\) going from galactic to extragalactic HII regions.
We apply an uniform methodology of a functional form of the structure function to characterize the turbulent using the velocity field variance, $\sigma^2$, autocorrelation length, \(r_0\), and power-law slope, \(m\).
Our results are compared with physical properties of each region and with previous investigations.

@@

Previous works that apply a statistical analysis on the velocity field of HII regions  
tend to consider just one region.
With the aim to develop a more complete study we choose 9 objects in the \halpha\ emission line.
This give us the opportunity to compare for first time the structure function of various objects following the same methodology.
We use previous published observational data to measure characterize the velocity field o HII regions located in the Milky Way, the Magellanic clouds and in the M 33 and NGC 6822 galaxies. 
Figure \ref{fig:hii-regions} shows the images of our sample.
Table \ref{tab:Reg} shows the names with the physical properties of interest in each region.

@@

Orion (M42) is the prototype galactic HII region and one on the best objects studied in the sky.
Located at a distance of 440 pc \citep{2008AJ....136.1566O} its main physical and kinematics properties, along its stellar population are documented in \citet{2001ARA&A..39...99O}.
The main ionizing star is \(\theta^{1}\)Ori C (spectral type \(\sim\)O7) and with other 3 B-type stars they form the Trapezium cluster.
The position of Orion near the side of the Orion Molecular Cloud (OMC-1) make it an ongoing star formation region and a example of a blister HII region. Some of these young stars are accountable for stellar jets and Herbig-Haro objects seen in the nebula \citep{arthur2016turbulence}.

The Carina nebula is a large star-forming complex located at a distance of 2 350 pc \citep{2006ApJ...644.1151S}.
Young clusters like Trumpler 14 and 16, and Collinder 228 together form the Car OB1 association.
This OB association has more than 65 stars earlier than B0, and several Wolf-Rayet stars.
The most star is a luminous blue variable, $\eta$ Car \citep{Damiani:2016a}.
As a star formation region,it presents several phenomena related with young stars as: evaporating protoplanetary discs, erosion of large dust pillars and the triggering of a second generation of embedded stars, Herbig-Haro objects, to mention some, \citet{2008hsf2.book..138S} and reference therein.
An approaching and receding kinematics components are known in the nebula.

The Lagoon Nebula (M8, NGC6523) is located at a distance of 1 250 pc \citep{2005A&A...430..941P} and contains the young stellar cluster NGC6530.
The region is illuminated by different massive stars of spectral types O and B, the hottest being 9 Sgr, type O4V \citep{Damiani:2017b}.
Optically, the brightest part of the nebula is called 'Hourglass nebula' which surrounds and obscures the star Herschel 36, type O7 \citep{1986AJ.....91..870W}. 
The velocity field shows several expanding shells, related to the cluster NGC 6530, the O stars 9 Sgr and Herschel 36, and the massive protostar M8East-IR. A blueshifted, neutral layer is also in very good agreement with predictions of champagne-flow models of blister HII regions \citep{Damiani:2017b}. The properties of the nebula are reviewed by \citet{2008hsf2.book..533T}.

The Tarantula Nebula (30 Doradus) is a luminous star-forming region in the LMC (Large Magellanic Cloud) and is the most luminous complex in the Local Group \citep{1984ApJ...287..116K}. The nebula is located at a distance of 49.9 kpc \citep{2013Natur.495...76P}.
It host the star forming region NGC 2070 that contains the massive star cluster R136. 
The star formation rate gas increased recently, 1-3 Myr ago \citep{2016ApJ...833..154C}, and the central ionized region spans for 40 pc.
This nebula is used as a comparison for extragalactic star-forming regions.

NGC 346 is the most active star-formation region in the SMC (Small Magellanic Cloud) located at a distance of 62 kpc \citep{2001ApJ...562..303D}. 
It has more than 30 O stars that ionize N66, the largest HII region \citep{2011ApJ...740...10D}.
\citet{2008ApJ...688.1050G} propose an expanding H II region or bubble blown by the winds of the massive progenitor as a mechanism that shapes the recent star formation in this region in addition to the photoionizing process of the OB stars. 
This mechanism is similar to shell-like H ii regions, with a central cluster in a cavity, and with ongoing star formation triggered around their periphery.

The dwarf irregular galaxy, NGC 6822, is located at a distance of 500 kpc (1'' = 2.4 pc) \citep{2012A&A...540A.135S} and the brightest HII regions are Hubble X and Hubble V (HX and HV hereafter).
HV has a characteristic length of 100 pc and a luminosity at its core of in L$_{H_\alpha}$ = 1 $\times$ 10$^{49}$ H$\alpha$ photons s$^{-1}$ \citep{1999PASP..111.1382O}.
HX has a characteristic length of 140 pc and a luminosity at its core of in L$_{H_\alpha}$ = 2.4 $\times$ 10$^{49}$ H$\alpha$ photons s$^{-1}$ \citep{1999PASP..111.1382O}.
Two recognized OB associations \citep{1991ApJ...379..621H,1992AJ....104.1374W} are identified within the region of HV and HX. HV is located near 'Hodge OB 8', and HX is located near 'Hodge OB13'  \citep{1999PASP..111.1382O}.

NGC 604 is the brightest giant HII region in the M33 galaxy visually dominated by a big loop, many shells and different size filaments.
It is located at the distance of 840 kpc (1'' = 4.1 pc) \citep{2015KamKinematics} with a length of 400 pc.
It has a luminosity in L$_{H_\alpha}$ = 10$^{39.42}$ erg s$^{-1}$ \citep{2002MNRAS.329..481B} and in L$_{X}$=9.3$\times$ 10$^{35}$ erg s$^{-1}$ \citep{2008ApJ...685..919T}.
\citet{2012ApJ...761....3M} derive an average age of 4$\pm$1 Myr and a total stellar mass of 1.6$^{+1.6}_{-1.0} \times$ 10$^{5}$M$_{\odot}$ for the region.
The stellar population has been identified and classified by \citet{1996ApJ...456..174H} (and references therein).
Recently, \citet{2011MNRAS.411..235E} focused on studying the Wolf-Rayet (WR) and red super giants (RSGs) stars population.
\citet{2012AJ....143...43F} focused on the massive young stellar objects (MYSOs).
The average ages for the stars, was determined to be from 3 to 5 Myr \citep{1996ApJ...456..174H} and with the RSGs as an older population have an age of 12.4 $\pm$ 2.1 Myr \citep{2011MNRAS.411..235E}.
This suggest that two episodes of star formation, at least, have taken place in the GEHR.
%\citep{1984A&A...141...49H} identified a gradient from the west to the SE of the nebula of 30 km s$^{-1}$.

NGC 595 is the second brightest giant HII region in the M33 galaxy.
%The electronic temperature is 7,670 $\pm$116 K \citep{2010MNRAS.402.1635R}.
\citet{1983A&A...119..185V} made an estimate of the total masses of HI and HII in the nebula to obtain values of M$_{HI}=$ 1.2 $\times$ 10 $^{6}$ M$_{\odot}$ and M$_{HII} =$ 4.6 $\times$ 10 $^{5}$ M$_{\odot}$, and a ionizing luminosity of the star cluster is estimated at 5 $\times$ 10$^{50}$ erg s $^{1}$.
\citet{1996AJ....111.1128M} estimate an age of 4.5 Myrs consistent with \citet{1993AJ....105.1400D}.
It has approximately 250 stars of the OB type, 13 Supergiants and 9 WR \citep{1996AJ....111.1128M}, ten WRs confirmed with spectroscopy \citet{1993AJ....105.1400D}, nine of the WN type and a WC, located near the bright core of the region.

\subsection{Observations}

We use data from \citet{1987A&A...176..347H} and \citet{arthur2016turbulence} to study of turbulence in the Orion Nebula.
\cite{1987A&A...176..347H} observations were obtained using a 106 cm-Cassegrain telescope at Observatorium Hoher List. 
A Fabry-Pérot interferometer was used with a étalon a separation of 0.5 mm. 
Interferograms have been taken with different pointing directions of the telescope's optical axis in the nebula. 
The exposures are overlapped and fall into one square of a grid with a width of 1' centered at \(\theta^{1}\)Ori C.

\citet{arthur2016turbulence} observations were initially published by \citet{2008RMxAA..44..181G}. 
The data was obtained with the echelle spectrograph attached to the 4 m telescope at Kitti Peak National Observatory (KPNO).
These observation cover 3 \(\times\) 5 arcmin\(^{2}\) of the central (Huygens) part of the Orion nebula.
The data consist of 96, North-South orientated 300 arcsec slits at 2 arcsec intervals with a width of 0.8 arcsec with a velocity resolution of 8 km s\(^{-1}\).

Archival data from \citet{Damiani:2016a} and \citet{Damiani:2017b} are use to study the Carina nebula and Lagoon nebula, respectively. 
The ESO VLT/FLAMES multi-fiber spectograph \citep{2002Msngr.110....1P} was used for these observations (Gaia-ESO Survey internal release \(iDR4\)). 
The Survey targets are low-mass stars ranging down to magnitude V \(\sim\) 18.5.
Mainly the spectra were obtained with the spectographs Giraffe (HR15N setup \(R \sim19 000\), wavelength range 6444-6818 \AA) and the UVES (setup 580, R \(\sim\)4700, range 4768-6830 \AA).

Using observations from \citet{Castro:2018a} (private communication) we study 30 Dor.
NGC 2070 was observed as part of the MUSE SV (Science Verification) programme at the Very Large Telescope (VLT) in August 2014, when the instrument was new. 
Four overlapping fields, each with an individual field of 1' \(\times\) 1' and a pixel scale of 0.2''/pixel were observed with exposure times of 4 \(\times\) 10s, 4 \(\times\) 60s, and 4 \(\times\) 600s. 
The table 1 on their work summarize the propertie of each field.
The data were reduced using the MUSE pipeline based on ESOREX recipes, with final astrometric calibration using the catalog of \citet{1999A&A...341...98S}. 
The final spectra span 4595-9366 \AA, with a resolving power of \(R \sim3 000\) around \halpha\  \citep{Castro:2018a}.

The archival data used in this work for the extragalactic giant regions, NGC 604, NGC 595, Hubble X and Hubble V was obtained with the Fabry Perot TAURUS-II instrument in the 4.2-m William Herschel Telescope (WHT) of del Roque de los Muchachos Observatory (ORM) in La Palma, Spain and was retrieved from the La Palma archive\footnote{\url{http://casu.ast.cam.ac.uk/casuadc/ingarch}}.
\citet{sabalisck1995supersonic} mentioned the main aspects of the observations (1990 July 31).
The two-dimensional imaging spectroscopy was captured using an IPCS-II detector and the 125 $\mu$m etalon.
The cumulative integration time per frame is 36 s with a seeing value of 1''.
The format of the data cube was of 256*256*100 with a spatial scale of 0.26 pixel$^{-1}$.
Finally, the reduction and analysis was done with the packages TAUCAL y TAUFITS \citep{1992ASPC...25..445L}. The NGC 604 TAURUS-II observations were used by \citet{sabalisck1995supersonic}, \citet{tanco1997} and \citet{2019arXiv191203543M}.

\begin{table*}
\begin{center}\caption{Summary of properties.}
\begin{tabular}{ccccc}\hline
HII       &  Distance (D)          & Diameter (R) & log L(H$_{\alpha}$) &  \(\langle \sigma_{LOS} \rangle \) \\
Region    &  [kpc]          &  [pc]    &  [erg/s]            &    [km/s]  \\ 
\hline
Orion small   & 0.436$\pm$0.02  & 0.6  &    37               &   6.0      \\
Orion large   & 0.436$\pm$0.02  & 5    &    37               &   6.0      \\ 
Lagoon    & 1.25$\pm$0.12   & 25       &    37.47            &   13.6     \\
Carina    & 2.35$\pm$0.05   & 15       &    39.6             &   22.4     \\
30 Dor    & 49.97$\pm$0.19  & 98.9     &    39.76            &   31.7     \\
NGC 346   & 61.9$\pm$1.1    & 64       &    38.67            &   10.2     \\
Hubble X  & 490$\pm$40      & 160      &    38.6             &   13.4     \\
Hubble V  & 490$\pm$40      & 130      &    38.87            &   12.3     \\
NGC 604   & 820$\pm$30      & 400      &    39.65            &   16.2     \\
NGC 595   & 820$\pm$30      & 400      &    39.36            &   18.3     \\
\hline
\end{tabular}\label{tab:Reg}
\end{center}
\end{table*}

%2013ApJ...773...69G M33 dist
% \citep{1984ApJ...287..116K} \citep{1986ApJ...300..624R}
